Energy and the CES production function

### 2015-08-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Rearrange tables. Add subsections.
Cleaning up code for historical data graph.

<<model_points>>=
model_points_style <- function(p) {
  p + 
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
}
@

@@

@@

<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
# Melt the data into a form that is useful in a couple places
### Don't write comments like that.  Say what you are doing to reshape and why.  
### I figured you were going to use it and don't need a comment for that.
### But it not at all easy to glance at this and see what the point is.

@@

histDataForGraph <- 
  leaf_apply(formulas, class = "formula", f=function(form, name){
    meta <- strsplit(name, split="[.]")[[1]] # %>% unlist  ### Why use unlist() here?
    Country <- meta[1]
    flavor <- meta[2]
    measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
    ### Is there any reason to select away some of the columns?
    trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]

    # return this.  ### No need to name and store it.
    melt(trimmed_historical_data, measure.vars = measure.vars, 
         value.name = "value", variable.name = "variable") %>%
    mutate(
        Country = Country,
        flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted")
      )
  }
  ) %>% bind_rows()

# Change variable names to make a nicer-looking graph and relevel factors before plotting
### Note: You an also change the order of things in the legend without changing the order in the data.

histDataForGraph <- 
  histDataForGraph %>% 
  mutate( variable = plyr::mapvalues(
    variable,
    from=c("iGDP", 
           "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
           "iL", "ihLest",
           "iXpMP", "iXp", "iUMP", "iU"),
    to=c("y", 
         "k", "k", "k", "k",
         "l", "l",
         "e", "e", "e", "e")),
    Country = relevelFactor(factor(Country), c("PT", "UK")),
    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
    variable = relevelFactor(factor(variable), unique(variable)) 
  )

### I think this exhibits poor use of white space.  See alternative below. 
if (FALSE)
historicalPlot(histDataForGraph, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ flavor, 
               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
  coord_cartesian(ylim=c(0.5, 13)) +
  xlab("") + 
  ylab("Indexed (1960=1)")

### Here each summand has the same indentation so you can see which things are being added together.
historicalPlot(
  histDataForGraph, 
  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
  facet_formula = Country ~ flavor, 
  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
coord_cartesian(ylim=c(0.5, 13)) +
xlab("") + 
ylab("Indexed (1960=1)")
@

@@

@@

%++++++++++++++++++++++++++++++
\subsection{Factor shares} 
\label{sec:shares}
%++++++++++++++++++++++++++++++

>>>>

<<model_points_style>>=
model_points_style <- function(p) {
  p + 
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
  scale_shape_manual(values = c(21, 21, 23:27)) +
  guides( 
    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
}
@

@@

%++++++++++++++++++++++++++++++
\subsection{Historical data} 
\label{sec:historical_data_graph}
%++++++++++++++++++++++++++++++

@@

<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=

@@

histDataForGraph <- 
  leaf_apply(formulas, class = "formula", f=function(form, name){
    meta <- strsplit(name, split="[.]")[[1]]
    Country <- meta[1]
    flavor <- meta[2]
    measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
    ### Is there any reason to select away some of the columns?
    trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]

    # return this.  ### No need to name and store it.
    melt(
      trimmed_historical_data, 
      measure.vars = measure.vars, 
      value.name = "value",
      variable.name = "variable") %>%
    mutate(
      Country = Country,
      flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
      variable = as.character(variable, stringsAsFactors=FALSE) # eliminate factors which cause problems with bind_rows() below.
      )
  }
  ) %>% 
  bind_rows() %>%
  # Change variable names to make a nicer-looking graph and relevel factors before plotting
  mutate( variable = plyr::mapvalues(
    variable,
    from=c("iGDP", 
           "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
           "iL", "ihLest",
           "iXpMP", "iXp", "iUMP", "iU"),
    to=c("y", 
         "k", "k", "k", "k",
         "l", "l",
         "e", "e", "e", "e")),
    Country = relevelFactor(factor(Country), c("PT", "UK")),
    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
    variable = relevelFactor(factor(variable), unique(variable)) 
  )

historicalPlot(
  histDataForGraph, 
  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
  # facet_formula = Country ~ flavor, 
  facet_formula = flavor ~ Country, 
  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
xlab("") + 
scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
ylab("Indexed (1960=1)")
@

@@

%++++++++++++++++++++++++++++++
\subsection{Residual plot} 
\label{sec:residual_plot}
%++++++++++++++++++++++++++++++

@@

%++++++++++++++++++++++++++++++
\subsection{Output elasticities} 
\label{sec:output_elasticities_graph}
%++++++++++++++++++++++++++++++
